### 2023-06-14 Conference Submission/SynthDataDiagrams/symbreg.tex
Final Thesis Copy

\documentclass{standalone}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta,positioning}

\begin{document}
\begin{tikzpicture}[
    mycircle/.style={
        circle,
        draw=black,
        fill=black,
        fill opacity = 1,
        inner sep=0pt,
        minimum size=5pt,
        font=\small},
    nocircle/.style={
        circle,
        draw=black,
        fill=black,
        fill opacity = 1,
        inner sep=0pt,
        minimum size=0.45pt,
        font=\small},
    targetcircle/.style={
        circle,
        draw=red,
        fill=red,
        fill opacity = 1,
        inner sep=0pt,
        minimum size=5pt,
        font=\small},
    myarrow/.style={->},
    dottedarrow/.style={-,dashed},
    thicccarrow/.style={->,line width=5pt},
    node distance=1.2cm and 1.5cm
]

@@

        \node[draw,text width=4cm] (c) at (5.5,-6.5) {Creates a tournament to test the fitness of each equation. The most fit equation is selected to go be rerandomised with a probability $p$, the next most fit is selected with probability $p(1-p)$};

        \node[draw,text width=4cm] (d) at (5.5,-0.5) {Rerandomises the selected equation to generate a new set of candidate equations};

>>>>

\documentclass{standalone}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{tikz}

\usetikzlibrary{decorations.markings}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta,positioning}

\begin{document}
\begin{tikzpicture}[
    mycircle/.style={
        circle,
        draw=black,
        fill=black,
        fill opacity = 1,
        inner sep=0pt,
        minimum size=5pt,
        font=\small},
    nocircle/.style={
        circle,
        draw=black,
        fill=black,
        fill opacity = 1,
        inner sep=0pt,
        minimum size=0.45pt,
        font=\small},
    targetcircle/.style={
        circle,
        draw=red,
        fill=red,
        fill opacity = 1,
        inner sep=0pt,
        minimum size=5pt,
        font=\small},
    myarrow/.style={->, -{Latex[length=3mm, width=2mm]}},
    dottedarrow/.style={-,dashed},
    thicccarrow/.style={->,line width=5pt},
    node distance=1.2cm and 1.5cm
]

@@

        \node[draw,text width=4cm] (c) at (5.5,-6.5) {Creates a tournament to test the fitness of each equation. The most fit equation is selected to go be re-randomised with a probability $p$, the next most fit is selected with probability $p(1-p)$};

        \node[draw,text width=4cm] (d) at (5.5,-0.5) {Re-randomises the selected equation to generate a new set of candidate equations};
